---
title: "Report Demo"
date: "September 6, 2016"
output: html_document
---

# Data
Load the data for this assignment into your R session with the following command:

```{r}
load(url("http://courseweb.lis.illinois.edu/~jguo24/SFTemps.rda"))
```

Check to see that the data were loaded by running:

```{r}
objects()
```
This should show five variables: dates, dayOfMonth, month, temp, and year

Use the length() function to find out how many observations there are.
```{r}
length(temp)
```

# Exercises

1. What was the coldest temperature recorded in this time period?
```{r}
# Example code
2+2
```

The coldest temperature is 4.

***
5. We would like to convert the temperature from Farenheit to Celsius. Below are several attempts to do so that each fail. 

    Try running each expression in R. 
    Record the error message in a comment
    Explain what it means. 
    Be sure to directly relate the wording of the error message with the problem you find in the expression.
*(1 pt)*

eval=FALSE tells R to not evaluate the code chunk, otherwise we flag an error and the document won't knit.
```{r,eval=FALSE}
(temp -32)
```
error message...  
explanation...

7. Run the following code to make a plot. (don't worry right now about what this code is doing)

```{r}
plot(temp~dates, col = rainbow(12)[month], type="p", pch=19, cex = 0.3)
```

Use the Zoom button in the Plots window to enlarge the plot.
Resize the plot so that it is long and short, so it is easier to read.
Include this plot in the homework your turn in. *(1 pt)*

[Look here for how to include an image (and other useful tips)](http://rmarkdown.rstudio.com/authoring_basics.html)